Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-17 vesicle_code/docs/adhesion/adhesion.tex
updated Figures 8 and 9

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced
  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
  the separation distance is $\delta = 0.4$, and the extension rate is
  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
  square, is the stagnation point.}
  \end{figure}

@@

%\begin{figure}[htp]
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
%   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
%  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
%  flow with an initial inclination angle $\theta=\pi$.  The reduced
%  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
%  the separation distance is $\delta = 0.4$, and the extension rate is
%  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
%  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
%  square, is the stagnation point.}
%  \end{figure}

 \begin{figure}
    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced area
  is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
  separation distance is $\delta = 0.4$, and the extension rate $\chi
  = 0.1$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

>>>>

\begin{figure}[htp]
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi2em2_ra070_tension_image05.png}
    \\
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi7em2_ra070_tension_image05.png}
    \\
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra070_tension_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced
  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
  the separation distance is $\delta = 0.4$, and the extension rate is
  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
  square, is the stagnation point.}
  \end{figure}

@@

 \begin{figure}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image01.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image02.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image03.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 4cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image04.png}
  \includegraphics[height = 0.18\textwidth,trim={4cm 1cm 3cm 1cm},clip]
    {figs/extensional_adR4em1adS7em1Chi1em1_ra080_tension_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced area
  is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
  separation distance is $\delta = 0.4$, and the extension rate $\chi
  = 0.1$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}
